---
title: "Quantitative Management Assignment-2 "
author: " karthikeyan Ramesh"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
#install.packages("lpSolve")
library("lpSolve") #Activating the lpSolve Package
```

Further going down in order to solve the problem we need to define the objective, constraints, direction and constants

Objective Function
$$ \text{The Objective function of } Max \hspace{.3cm} Z = 420 (B_1L+B_2L+B_3L) + 360 (B_1M+B_2M+B_3M) + 300 (B_1S+B_2S+B_3S) $$
$$\text{Subject to}$$
$$ B_1L+B_1M+B_1S \le 750 $$
$$ B_2L+B_2M+B_2S \le 900 $$
$$ B_3L+B_3M+B_3S \le 450 $$\\
$$ 20B_1L+15B_1M+12B_1S \le 13000 $$
$$ 20B_2L+15B_2M+12B_2S \le 12000 $$
$$ 20B_3L+15B_3M+12B_3S \le 5000 $$\\
$$ B_1L+B_2L+B_3L \le 900 $$
$$ B_1M+B_2M+B_3M \le 1200 $$
$$ B_1S+B_2S+B_3S \le 750 $$
Non Negativity Constraints
$$ B_1L,B_2L,B_3L,B_1M,B_2M,B_3M,B_1S,B_2S,B_3S \ge 0 $$
The  constraints for 
$$ B_1L+B_1M+B_1S+0B_2L+0B_2M+0B_2S+0B_3L+0B_3M+0B_3S \le 750       $$
$$ 0B_1L+0B_1M+0B_1S+B_2L+B_2M+B_2S+0B_3L+0B_3M+0B_3S \le 900$$
$$ 0B_1L+0B_1M+0B_1S+0B_2L+0B_2M+0B_2S+B_3L+B_3M+B_3S \le 450$$
$$ 20B_1L+15B_1M+12B_1S+0B_2L+0B_2M+0B_2S+0B_3L+0B_3M+0B_3S \le 13000 $$
$$ 0B_1L+0B_1M+0B_1S+20B_2L+15B_2M+12B_2S+0B_3L+0B_3M+0B_3S \le 12000 $$
$$0B_1L+0B_1M+0B_1S+0B_2L+0B_2M+0B_2S+20B_3L+15B_3M+12B_3S \le 5000 $$
$$B_1L+0B_1M+0B_1S+B_2L+0B_2M+0B_2S+B_3L+0B_3M+0B_3S \le 900$$
$$0B_1L+B_1M+0B_1S+0B_2L+B_2M+0B_2S+0B_3L+B_3M+0B_3S \le 1200$$
$$0B_1L+0B_1M+B_1S+0B_2L+0B_2M+B_2S+0B_3L+0B_3M+B_3S \le 750$$

The Objective Function 
```{r}
f.obj <- c(420,360,300,420,360,300,420,360,300)
```

The Constraints 
```{r}
f.con <- matrix(c(1,1,1,0,0,0,0,0,0,
                  0,0,0,1,1,1,0,0,0,
                  0,0,0,0,0,0,1,1,1,
                  20,15,12,0,0,0,0,0,0,
                  0,0,0,20,15,12,0,0,0,
                  0,0,0,0,0,0,20,15,12,
                  1,0,0,1,0,0,1,0,0,
                  0,1,0,0,1,0,0,1,0,
                  0,0,1,0,0,1,0,0,1), nrow = 9, byrow=T)
```

The Direction of the constraints
```{r}
f.dir <- c('<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=',
           '<=')
```

The constants for right hand side values
```{r}
f.rhs <- c(750,900,450,13000,12000,5000,900,1200,750)
```

The lp function to solve the problem basing the objective function 
```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)
```
The lp function of the values for the variables 
```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)$solution
```
