---
title: "QMM-Assignment-6"
author: "Karthikeyan ramesh"
date: "2022-11-20"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r comment=NA }
library(lpSolve)
library(lpSolveAPI)
y <- read.lp("ass10.lp")
y
```

Solving the problem to get objective function. 
```{r}
solve(y)
get.objective(y)
```
#Our Objective function is: 25675.
#Let's examine the factors to determine what this means..

```{r}
get.variables(y)
```


### What it illustrates is:
#X1 = shift 1 with Sunday and Monday off = 2
#X2 = shift 2 with Monday and Tuesday off = 4
#X3 = shift 3 with Tuesday and Wednesday off = 5
#X4 = shift 4 with Wednesday and Thursday off = 0
#X5 = shift 5 with Thursday and Friday off = 8
#X6 = shift 6 with Friday and Saturday off = 1
#X7 = shift 7 with Saturday and Sunday off = 13

### Our goal-oriented purpose = 2x775 + 4x800 + 5x800 + 8x800 + 1X775 + 13x750 = 25675.
### The bare least that we can afford to pay for salary is 25675.